---
title: "Flatiron cleaning"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 1px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```
<br>

***

```{r library, include=FALSE}
library(drake)
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
```

```{r loadd}
loadd(drugs)
creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
```


# `r emo::ji("question_mark")` Reminders of each capping and formula:  

Creatinine data are capped as :  
- creat < 0.7 was set at 0.7  
- creat > 3 are eliminated  

CrCl calculation :

$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>


Calculating more BSA values :
$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
<br>

I clean the data up by keeping the `relativeorderedamount`:  
- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
- >= 2  & <= 6   for platin and with a unit in `AUC`

<br>

`expected_dose` is:  
-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin). 

<br>

Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$

<br>

<span style="color:red">**Please confirm everything is correct**</span>  

***
At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
- exclude the patients who had surgery but we don't have a date  
- exclude patients whose histology is unknown  
- exclude patients who didn't survive 1 month  

Also height, weight, bsa, creatinine is cleaned and ready. Creatinine minimum is now capped at 0.7 and not 0.8.  
Creatinine clearance maximum is capped at 125.  

Now drug cleaning!

# I. Drug episode questions

**We start with a number of patient who has drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**  

### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" & 
           ismaintenancetherapy == "FALSE") %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()
```
We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis. Patients left :

```{r}
drugs1 <- drugs1 %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )
drugs1 %>% distinct(patientid) %>% nrow()
```

### step 2: 90 days rule between diagnosis and treatment

Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
```{r}
remove_90daysrule <- drugs1 %>% 
  filter((days_at_first_drug > 90 | days_at_surg > 90)) %>% 
  distinct(patientid)
remove_90daysrule <- paste(remove_90daysrule$patientid, collapse = "|")

drugs1 <- drugs1 %>% 
  # remove these patients who 90 days rule
  filter(!str_detect(patientid, remove_90daysrule))

drugs1 %>% distinct(patientid) %>% nrow()
```

### step 3: 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis

This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal. 
```{r}
# drugs1 %>% 
#   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
#            duration(n=1, units = "days"), 
#          thirty_days_exclusion = case_when(
#            thirty_days_exclusion <= 30                  ~ "Exclude"
#          )) %>% 
#   filter(thirty_days_exclusion == "Exclude") %>% 
#   distinct(patientid) %>% 
#   nrow

drugs1 <- drugs1 %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days"), 
         thirty_days_exclusion = case_when(
           thirty_days_exclusion <= 30                  ~ "Exclude",
           thirty_days_exclusion > 30                   ~ "Include",
           is.na(dateofdeath)                           ~ "Include"
         )) %>% 
  filter(thirty_days_exclusion != "Exclude")

# drugs1 %>% distinct(patientid) %>% nrow()

```
In the data, `r drugs1 %>% mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/duration(n=1, units = "days"), thirty_days_exclusion = case_when(thirty_days_exclusion <= 30~ "Exclude")) %>% filter(thirty_days_exclusion == "Exclude") %>% distinct(patientid) %>% nrow` are excluded so we still have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.

### step 4: Exclude exclude == "1" coded by Lauren

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
Patients left after this step:

```{r}
drugs1 <- drugs1 %>% 
  filter(exclude != "1")

drugs1 %>% distinct(patientid) %>% nrow()
```

<!-- ### step .: Remove linename that doesn't include platin or taxanes in first line -> later in the process, need first to recode linenumber with all the drugs in. -->
```{r}
# drugs1 <- drugs1 %>% 
#   # 2. Filtering----
#   filter(episodedatasource == "Administrations" & 
#            # ismaintenancetherapy == "FALSE" & 
#            !is.na(amount) &
#            (days_at_first_drug < 60 | days_at_surg < 60) &
#            
#            days_at_first_drug >= 0 &
#            (is.na(surgerydate) | days_at_surg >= 0)
#          )

# drugs1 %>% 
#   filter(linenumber == 1) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
```

### step 5: Remove chemotherapy only patients
```{r}
drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))
drugs1 %>% distinct(patientid) %>% nrow()
```


### step 5: Combine multiple administrations of the same drug at the same date
```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
  
  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>% 
  
  mutate(drugname_type = case_when(
    str_detect(drugname, "platin")       ~ "platin",
    str_detect(drugname, "taxel")        ~ "taxel"
  ))
```

### step 6: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = 
           factor(chemotherapy_type, levels = 
                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>% 
  
  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
  ungroup() %>% 
  
  group_by(patientid, chemotherapy_type) %>% 
  mutate(linenumber_adj = dense_rank(linenumber_new)) %>% 
  ungroup() %>% 
  # 6.Add a 30 day rule to switch linenumber----
  # group_by(patientid, linenumber_new) %>% 
  # arrange(episodedate) %>% 
  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
  # ungroup() %>% 
  # group_by(patientid) %>% 
  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
  
  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor))

# Number of patient with a jump line in the first line # 60 would have
# therapy_line %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   arrange(desc(jump_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(jump_line) %>% 
#   tbl_summary()
```

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(chemotherapy_type, therapy, treatment_sequence) %>% 
  tbl_summary(by = therapy)
```

### How many lines did patients received as Neoadjuvant
`r emo::ji("question_mark")`  
Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.  

```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```

### step 8: Remove patients with more than 1 line as Neo
We are removing the 34 patients who received multiple Neoadjuvant line.   
`r emo::ji("check")`  

<!-- Here the lines for the 34 patient. -->
```{r, rows.print = 40}
# therapy_line %>% 
#   filter(chemotherapy_type == "Neoadjuvant" &
#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
#   arrange(patientid, episodedate) %>% 
#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
#   select(-linenumber)

remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # Remove patients with more than 1 line as Neo
  filter(!str_detect(patientid, remove_morethan1_neo))
```

Patients left:
```{r}
therapy_line %>% distinct(patientid) %>% nrow()
```

### step 7: Remove linename that doesn't include platinum or taxanes in first line

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    

```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>% 
  
  mutate(remove_linename_other = case_when(
    # keep these drugs in line 1 of upfront chemo and upfront surg
    # linenumber_new == 1 & 
    #   drug_count == 1 &
    #    !str_detect(linename, "platin|taxel")                                 ~ "remove",
    # linenumber_new == 1 &
    #   drug_count == 2 &
    #   (
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    #   )                                                                      ~ "remove",
    # linenumber_new == 1 &
    #   drug_count >= 3 &
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    # 
    #                                                                          ~ "remove",
    # weird one
    linenumber_new == 1 &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo|lumab|Tra|ximab|zole|Aza|trex|Gos|lide|Pem")                       
                                                                         ~ "remove",
    linenumber_new == 1 & linename == "Bevacizumab"                      ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo")                       
                                                                         ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
    # keep these drugs in line 2 of upfront chemo from when line switch
    # linenumber_new == 2 &
    #   therapy == "Upfront Chemo" &
    #   drug_count == 1 &
    #    !str_detect(linename, "platin|taxel")  ~ "remove",
    #   
    #   
    # linenumber_new == 2 &
    #   therapy == "Upfront Chemo" &
    #   drug_count == 2 &
    #   (
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    #   ) ~ "remove",
    #   
    #   
    # linenumber_new == 2 &
    #   therapy == "Upfront Chemo" &
    #   drug_count >= 3 &
    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
    #   # !str_detect(linename, "taxel") &
    #   # !str_detect(linename, "Bev")
    #                     ~ "remove",

    TRUE                                           ~ NA_character_
  )) %>% 
  # group_by(patientid) %>% 
  # fill(remove_linename_other, .direction = "down") %>% 
  # ungroup() %>% 
  arrange(patientid, episodedate) #%>% 

remove_linename_other <- remove_linename_other %>% 
  filter(remove_linename_other == "remove") %>% 
  distinct(patientid, .keep_all = T)


# remove_linename_other# <- therapy_line %>% 
  # filter(chemotherapy_type == "Neoadjuvant" &
  #          linenumber_new != 1)
remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")

# therapy_line %>% 
#   filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# therapy_line %>% 
#   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))

# therapy_line %>% distinct(patientid) %>% nrow()

therapy_line <- therapy_line %>% 
  # Remove patients with other linename
  filter(!str_detect(patientid, remove_linename_other)) %>% 
  arrange(patientid, episodedate)
# example of keep
```

First table is frontline Neo, second table is frontline Adj.
```{r}
therapy_line %>% 
  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

# therapy_line %>% distinct(patientid) %>% nrow()
```

We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.

### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
```{r Number of patient who switch line}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      therapy == "Upfront Chemo"                   ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()
```

Some patients had part of their first line switched to Adjuvant line. How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate, end = lineenddate)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_bar(color = "slateblue") +
  theme_minimal()+
  ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)
```

<!-- Easy example (sorry for the poor looking table `r emo::ji("face_with_raised_eyebrow")`):   -->
<!-- In this example, 1 cycle is switched from the initial line 1 coded by flatiron to a linenumber_new 2 -->

<!-- <br> -->

<!-- | linenumber (coded by flatiron) |  surgery |  linenumber_new that I coded   |  drug    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  | happened |             2                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             2                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->

<!-- <br> -->



<!-- Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.   -->
<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>   -->
```{r Number of patient who switch line2, rows.print=30}
# Problem F0000AD999ABF but would be good for F003F2BEEDB37
# therapy_line %>% 
#   filter(str_detect(patientid, "F41E15E18E008")) %>% 
#   arrange(patientid, episodedate) %>% 
#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
```

<!-- Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).     -->
<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron. <span style="color:red">**Is that correct?**</span>   -->
```{r, rows.print=30}
# therapy_line %>% 
#   filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
#   arrange(patientid, episodedate) %>% 
#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)

# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       treatment_sequence == "neo + surg + adj"     ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   filter(change_line == 1) %>% 
#   group_by(patientid) %>% 
#   mutate(firstdate = first(episodedate)) %>% 
#   mutate(lastdate = last(episodedate)) %>% 
#   ungroup() %>% 
#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
#   geom_histogram(binwidth = 7)+
#   theme_minimal()+
#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
#                      minor_breaks=c(10, 20, 30, 40)#,
#                      #labels = c(0, 50, 100, 150)
#   )
```
<!-- `r emo::ji("question_mark")`   -->
<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->

<br>



### step 9: Remove patients who switch drug within a line

`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin") %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.  
`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin") %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.  

Patients left:
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
# therapy_line %>% 
#   filter(str_detect(linename, "Car") &
#            drugname == "cisplatin") %>%
#   distinct(patientid) %>% nrow()
# 
# therapy_line %>% 
#   filter(str_detect(linename, "Cisplatin") &
#            drugname == "carboplatin") %>%
#   distinct(patientid) %>% nrow()

remove_switch <- therapy_line %>% 
  filter(
    (str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
  (str_detect(linename, "Cisplatin") & drugname == "carboplatin")
  ) %>%
  distinct(patientid)
remove_switch <- paste(remove_switch$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # remove these patients who switched C > C 
  filter(!str_detect(patientid, remove_switch))
therapy_line %>% distinct(patientid) %>% nrow()
```

```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
# therapy_line %>% 
#   filter(str_detect(linename, "Pacli") &
#            drugname == "docetaxel") %>%
#   distinct(patientid) %>% nrow()
# therapy_line %>% 
#   filter(str_detect(linename, "Doce") &
#            drugname == "Paclitaxel") %>%
#   distinct(patientid) %>% nrow()
```
`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel") %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
I am removing these patients for now but <span style="color:red">**Do we need to remove the patients that switch from paclitaxel to docetaxel and vice versa since the dosing calculating is the same for both?**</span>  


`r emo::ji("question_mark")`  

<span style="color:red">**Are you good with thatl?**</span>  

Patients left:
```{r}
remove_switch1 <- therapy_line %>% 
  filter(
    str_detect(linename, "Pacli") & drugname == "docetaxel"
  ) %>%
  distinct(patientid)
remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # remove these patients who switched C > C 
  filter(!str_detect(patientid, remove_switch1))
therapy_line %>% distinct(patientid) %>% nrow()
```

<br>

<!-- `r emo::ji("question_mark")`   -->
<!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->

### step 10: Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 

  arrange(patientid, episodedate) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline)) %>%
  mutate(cycle_drugname = case_when(
    cycle_count_perline == drugname_count_perline          ~ drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_drugname) %>%
  mutate(cycle_inc = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
  

  # + What to do when it is a cycle change F003F2BEEDB37 , 
  
  
  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_inc) %>% 
  group_by(patientid, linenumber_new) %>%
  mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>% 
  
  group_by(patientid, linenumber_new) %>% 
  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  
  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  mutate(n = row_number(drugname)) %>%

  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  fill(base_days_between_cycle, .direction = "downup") %>% 
  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  group_by(patientid, linenumber_new) %>%
  mutate(drug_count_perline = n()) %>%
  mutate(skipped_cycle_indays1 = ifelse(
    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  group_by(patientid) %>% 
  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()
```


### step 11: Bind everything together and calculating target_auc and expected dose

(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column called `target_auc` for a tidy data organisation - You can find the calculations formula at the end of the document)  
When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, cisplatin and taxanes and their `expected_dose`. It can be days in between but it can also be more. 

`r emo::ji("check")`  
We decided to take the creatine, weight, bsa measured within a month and in the same cycle of the administration.

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    interval_creat < 31 &
      creat_date > linestartdate &
      creat_date < lineenddate             ~ interval_creat,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>% 
  
  # Merge with height
  left_join(. , height,  by = "patientid") %>%
  mutate(interval_height = abs(interval(start= height_date, end= cycle_start_date)/
           duration(n=1, unit="days"))) %>%
  arrange(interval_height) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  
  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    interval_weight < 31 &
      weight_date > linestartdate &
      weight_date < lineenddate             ~ interval_weight,
    TRUE                                    ~ NA_real_
  )) %>% 
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

  # Calculate bmi
  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
  mutate(bmi_cat = case_when(
    bmi_at_dx < 25                    ~ "Underweight and normal weight",
    bmi_at_dx >= 25 &
      bmi_at_dx < 30                  ~ "Overweight",
    bmi_at_dx >= 30                   ~ "Obese"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # Calculate CrCl
  inner_join(., clinical_data %>% select(-surgerydate),
             by = "patientid") %>% 
  mutate(CrCl = (
       (
    ((140 - ageatdx) * weight) /
    (72 * creatinine)
       ) *
    0.85)
  ) %>% 
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>% 

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    interval_bsa < 31 &
      bsa_date > linestartdate &
      bsa_date < lineenddate               ~ interval_bsa,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    interval_auc < 31 &
      auc_date > linestartdate &
      auc_date < lineenddate               ~ interval_auc,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>% 

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

```{r plot interval}
Treatment %>% 
  ggplot(aes(x= interval_creat)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_height)) +
#   geom_bar() +
#   coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_weight)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_bsa)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_auc)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
```

### If we keep as is, the
## **Number of patients in final dataset is `r Treatment %>% distinct(patientid) %>% nrow()`**

<br>

***

<br>

# A little of data analysis
## Explore the dataset

```{r}
analysis_data <- Treatment
```

Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
<br>

# Missingness
Here some representation of missingness in our data:  
- In the first plot (horizontal bar), `r is.na(analysis_data$height_at_dx) %>% sum()` data is missing for height closest to dx but `r analysis_data %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.   
- In the second plot (horizontal bar), `r is.na(analysis_data$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(analysis_data$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
```{r}
library(naniar)
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

analysis_data %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
  gg_miss_upset()

# is.na(analysis_data$CrCl) %>% sum()
# is.na(analysis_data$amount) %>% sum()
# is.na(analysis_data$target_auc) %>% sum()

# analysis_data %>% filter(is.na(amount)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
# 
# analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
```
If we remove patients who have at least 1 missing amount administered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.  

If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.  

# Analysis

## 1.Clinical summary table


<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r Table 1}
analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, 
           agecat, "ageatdx",
            
           bmi_at_dx, bmi_cat, 
           weight_at_dx, height_at_dx, bsa_at_dx,
           
           "histology", "stagecat",
           
           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
  tbl_summary() %>% bold_labels()
```

<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
```{r Table 2}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",
            
           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat",
           
           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown", 
           
           "hrd_tissue", "gis_tissue")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

***

<br>

<!-- # II.Analysis Treatment -->

## 1.Treatment summary table

<span style="color:green">**Table 3 Summary treatment data by race**</span>

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "debulking",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

***

<br>
<br>

***

<br>

# RDI calculation

RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.

```{r RDI calculation}
Frontline <- Treatment %>% 
  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
  #   group_by(patientid, chemotherapy_type) %>% 
  # mutate(linenumber_adj = dense_rank(linenumber_new)) %>% 
  
  
  filter(chemotherapy_type == "Neoadjuvant" |
           (chemotherapy_type == "Adjuvant" &
              linenumber_adj == 1)) %>%
  
  
  
  mutate(relative_dose_intensity = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ amount/expected_dose,
    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
  )) %>%
  
  
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>% 
  
  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))
```



```{r}
Frontline %>% distinct(patientid) %>% nrow()
```


# Analysis



## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= histology))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= stagecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_germline))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA gernline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_tumor))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = histology))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = stagecat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = agecat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_germline))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA germline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_tumor))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>
</div>

<br>

## 3.Survivals by clinical

<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>  

<div class = "row">
<div class = "col-md-6">
```{r clinical from dx, fig.height = 7}
# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>

<div class = "col-md-6">
```{r clinical from first treatment, fig.height = 7}
# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>
</div>

<br>
<br>

***

<br>

# II.Analysis Treatment

## 1.Treatment summary table

<span style="color:green">**Table . Summary treatment data by race**</span>

```{r treatment table}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
    ) %>% bold_p(t = .05)
# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

# Frontline %>% 
#   arrange(episodedate) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   group_by(chemotherapy_type) %>% 
#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
#   geom_bar(stat="identity")+
#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
#   theme_minimal()+
#   guides(fill = FALSE) +
#   coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  # group_by(treatment_sequence) %>% 
  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= treatment_sequence,
             # y= percent, 
             fill = treatment_sequence))+
  geom_bar(
    # stat="identity"
    )+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()

```
</div>

<div class = "col-md-6">
```{r}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()


Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  # group_by(treatment_sequence) %>% 
  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= raceeth,
             # y= percent, 
             fill = treatment_sequence))+
  geom_bar(
    position ="fill"
    )+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  # guides(fill = FALSE) +
  coord_flip()

# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= chemo))+
#   geom_bar()+
#   theme_minimal()+
#   coord_flip()
```
</div>
</div>

<br>

## 3.Survivals by treatment

<div class = "row">
<div class = "col-md-6">
```{r treatment survival, fig.height = 7}
# OS by extentofdebulking
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by residualdiseasestatus
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by treatment_sequence
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by therapy
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by extentofdebulking
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by residualdiseasestatus
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by treatment_sequence
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by therapy
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))
```
</div>
</div>

<br>
<br>

***

<br>


# III.RDI

## 1.RDI summary table

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>

```{r Table 4}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(relative_dose_intensity ~ 'continuous'),
              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              type = list(relative_dose_intensity ~ 'continuous'),
              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl8 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)





tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl8 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))


tbl_stack(list(tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
```
<br>


<br>

***

<br>

## 2.Plots RDI

<div class = "row">
<div class = "col-md-6">
```{r rdi plots}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_boxplot()+
  ylim(c(-.25, 3.5))+
  geom_jitter(shape=16)+
  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
  theme_minimal()+
  facet_wrap(.~ cycle_drugname)

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_violin()+
  ylim(c(-.25, 3.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= cycle_drugname, y= relative_dose_intensity, color = chemotherapy_type))+
  geom_violin()+
  ylim(c(-.25, 3.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()+
  coord_flip()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
  geom_bar()+
  theme_minimal()+
  facet_wrap(.~ chemotherapy_type)


```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  # geom_boxplot()+
  ylim(c(-.25, 3.5))+
  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
  theme_minimal() +
  guides(color=FALSE)+
  facet_wrap(.~ cycle_drugname)

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
  geom_violin()+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()+
  facet_wrap(.~ cycle_drugname)

# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= cycle_drugname, y= relative_dose_intensity))+
#   geom_violin(aes(color=relative_dose_intensity<0.85))+
#   ylim(c(-.25, 2.5))+
#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
#   theme_minimal()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
  geom_bar(position = "fill")+
  theme_minimal()+
  facet_wrap(.~ chemotherapy_type)


```
</div>
</div>

```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, alpha = relative_dose_intensity<0.85))+
  geom_violin(aes(fill = cycle_drugname))+
  ylim(c(-.25, 2.5))+
  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()+
  facet_wrap(.~ raceeth)
```

A quick summary for the RDI repartition
```{r}
Frontline2 <- Frontline# %>% filter(linenumber_new == "1")
summary(Frontline2$relative_dose_intensity)
```

<div class = "row">
<div class = "col-md-6">
```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
  geom_bar()+
  theme_minimal()+
  facet_wrap(.~ chemotherapy_type)
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
  geom_bar(position = "fill")+
  theme_minimal()+
  coord_flip()+
  facet_wrap(.~ chemotherapy_type)
```
</div>
</div>

<br>

## 3.Survivals by RDI

<div class = "row">
<div class = "col-md-6">
```{r rdi survival, fig.height = 7}
# OS by RDI_grp
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE) %>% 
#                      filter(exclude != "1")),
#            title = "OS from diagnosis Overall RDI", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
# 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by RDI_grp for platin
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
#                      
#                      distinct(patientid, .keep_all = TRUE)), 
#            title = "OS from diagnosis carboplatin", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
#                      
#                      distinct(patientid, .keep_all = TRUE)), 
#            title = "OS from diagnosis cisplatin", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by RDI_grp for taxel
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
#                      
#                      distinct(patientid, .keep_all = TRUE)), 
#            title = "OS from diagnosis all taxel", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# # OS by RDI_grp
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE) %>% 
#                      filter(exclude != "1")),
#            title = "OS from first treatment overall RDI", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by RDI_grp for platin
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
#                      
#                      distinct(patientid, .keep_all = TRUE)), 
#            title = "OS from first treatment carboplatin", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
#                      
#                      distinct(patientid, .keep_all = TRUE)), 
#            title = "OS from first treatment cisplatin", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by RDI_grp for taxel
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
#                      
#                      distinct(patientid, .keep_all = TRUE)), 
#            title = "OS from from first treatment all taxel", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
```
</div>
</div>

<br>

## Survivals RDI by chemotherapy type
**On the left are Neoadjuvant, on the right are Adjuvant**

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp for platin
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from first treatment carboplatin",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 2))

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from first treatment cisplatin",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 2))

# OS by RDI_grp for taxel
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
                     filter((exclude != "1") & str_detect(drugname, "taxel"),
                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from from first treatment all taxel",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp for platin
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
                            str_detect(chemotherapy_type, "Adjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from first treatment carboplatin",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 2))

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
                            str_detect(chemotherapy_type, "Adjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from first treatment cisplatin",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 2))

# OS by RDI_grp for taxel
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
                     filter((exclude != "1") & str_detect(drugname, "taxel"),
                            str_detect(chemotherapy_type, "Adjuvant")) %>%

                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from from first treatment all taxel",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 2))
```
</div>
</div>




<br>
<br>

***
# IV.Hazard Ratio

<span style="color:green">**Table 5 HR**</span>  
`coxph(Surv(time = month_at_os, event = vitalstatus)~variables`
```{r Table 5 HR}
# tbl1 <- Frontline %>%
#   select(bmi_cat) %>%
#   tbl_summary(#by = vitalstatus,
#               statistic = all_categorical() ~ "{Frontline %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
#               )
# tbl2 <- coxph(Surv(time = month_at_os,
#                      event = vitalstatus)~bmi_cat,
#                 data = Frontline) %>%
#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
#
# tbl_merge(list(tbl1, tbl2))
#
# coxph(Surv(time = month_at_os,
#                      event = vitalstatus)~RDI_grp,
#                 data = Frontline) %>%
#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()

# Frontline %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>%
# tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = Frontline$month_at_os, event = Frontline$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
#   bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")

tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
# tbl3 <- Frontline %>%
#   filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
# tbl3 <- tbl3 %>%
#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl1, tbl2),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant")) %>%
  bold_labels() %>%
  italicize_levels()
# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
tbl5 <- tbl5 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
# tbl6 <- Frontline %>%
#   filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
# tbl6 <- tbl6 %>%
#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl4, tbl5),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant")) %>%
  bold_labels() %>%
  italicize_levels()


tbl7 <- Frontline %>%
  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
tbl7 <- tbl7 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl8 <- Frontline %>%
  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
tbl8 <- tbl8 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
# tbl9 <- Frontline %>%
#   filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
# tbl9 <- tbl9 %>%
#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl7, tbl8),
          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant")) %>%
  bold_labels() %>%
  italicize_levels()

tbl10 <- Frontline %>%
  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
# tbl12 <- Frontline %>%
#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
# tbl12 <- tbl12 %>%
#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl10, tbl11),
          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

***
# V.Regression
## By clinical, demo
`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = Frontline, family = binomial)`
```{r regression}
# Regression vital status prediction
model <- glm(vitalstatus ~ bmi_at_dx + bmi_cat + #RDI_grp + 
               raceeth, data = Frontline %>% 
               distinct(patientid, .keep_all = TRUE), 
             family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

`glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = Frontline, family = binomial)`
```{r}
# model <- glm(vitalstatus ~ 
#                histology + tstage + brca1_tumor + brca2_tumor + 
#              issurgery +
#              chemotherapy_type, 
#              data = Frontline %>% 
#                distinct(patientid, .keep_all = TRUE), 
#              family = binomial)
# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)`
<!-- !!!! Prediction of RDI all drug together!!!! -->
```{r}
# Regression RDI prediction
# model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)
# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

### By drug
<!-- !!! But sometimes we had a switch between cisplatin/carboplatin -->
```{r}
#  for carbo
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

# tbl5 <-
  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))

#  for Cisplatim
# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
#                filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

# model <- glm(RDI_grp ~ agecat + bmi_cat, data = Frontline %>%
#                filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
# 
# # tbl5 <-
#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))

#  for taxel
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

# tbl6 <-
  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
```
<br>
<br>

***

<br>

<font size="10">Yay! `r  emo::ji("party_popper")`</font> 
    
***
























