---
title: "Flatiron analysis"
author: "Christelle Colin-Leitzinger"
date: "3/17/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
---

<style type="text/css">
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

# Analysis
***
<br>
For all these analysis, I excluded the patients Lauren said to remove from the analysis.

```{r library, include=FALSE}
library(drake)
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
```

```{r loadd}
loadd(clinical_data, vitals, drugs, auc, creatinine)
```

```{r}
#################################################################################################### I ### Basic Clinical Cleaning----
#################################################################################################### 1 ### Cleanup of creatinine----
creatinine <- creatinine %>%
  # remove creatine urine
  filter(str_detect(labcomponent, "blood|serum")) %>% 
  mutate(creatinine = case_when(
    testresultcleaned < 0.8        ~ 0.8,
    testresultcleaned > 3          ~ NA_real_,
    TRUE                           ~ testresultcleaned
  )) %>% 
  # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
  mutate(creatinine1 = case_when(
    testresult < 0.8               ~ 0.8,
    testresult > 3                 ~ NA_real_,
    TRUE                           ~ testresult
  )) %>% 
  mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
  filter(!is.na(creatinine)) %>% 
  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
  select(c("patientid", creat_date = "testdate", "creatinine", creat_units = "testunitscleaned"))

# body_surface_area, height and weight are all coming from vitals
vitals <- vitals %>% 
  mutate(testdate = as.Date(testdate, format = "%m/%d/%y"))


#################################################################################################### 2 ### Cleanup of BSA----
body_surface_area <- vitals %>% 
  filter(labcomponent == "Body Surface Area (BSA)") %>% # only 399 patients data
  # Limit max = 4.14, min = 0.418 calculated for biggest to smallest person
  mutate(testresult = ifelse(testresult < 0.418 | testresult > 4.14, NA_real_, testresult)) %>% 
  group_by(patientid) %>%
  # I used the median to remove outlier within a patient
  mutate(median_testresult = median(testresult)) %>% 
  ungroup() %>% 
  mutate(BSA = case_when(
    testresult > (median_testresult + 0.4) |
      testresult < (median_testresult - 0.4)      ~ NA_real_,
    TRUE                                          ~ testresult
  )) %>% 
  mutate(BSA = coalesce(testresultcleaned, BSA)) %>% 
  filter(!is.na(BSA)) %>% 
  mutate(BSA_units = "m2") %>% 
  select(c("patientid", bsa_date = "testdate", "BSA", "BSA_units"))


#################################################################################################### 3 ### Cleanup of Height----
height <- vitals %>% 
  filter(test == "body height") %>% 
  # To get more data, I have data from testresult that can be used
  # But need to fill up testunits, transfer in kg and coalesce.
  group_by(patientid) %>% 
  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
  ungroup() %>% 
  # Clean up outliers compare to tallest ans smallest record
  mutate(testresultcleaned = case_when(
    testresultcleaned > 231 | # Tallest women height
      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
                                     ~ NA_real_,
    TRUE                             ~ testresultcleaned
  )) %>% 
  mutate(testresult = case_when(
    testresult > 231 & testunits == "cm" |
      testresult < 100 & testunits == "cm" |
      testresult > 7.58 & testunits == "ft" |
      testresult < 3.28 & testunits == "ft" |
      testresult > 90.94 & testunits == "in" |
      testresult < 39.37 & testunits == "in"|
      testresult == 0
                                     ~ NA_real_,
    TRUE                             ~ testresult
  )) %>% 
  # Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
  group_by(patientid) %>%
  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
  ungroup() %>% 
  mutate(testresultcleaned_verified = case_when(
    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
    TRUE                                                      ~ testresultcleaned
  )) %>% 
  # select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified, 
  #          testunitscleaned, testunits, testresult)) %>% 
  
  group_by(patientid, testunits) %>%
  mutate(median_testresult = median(testresult)) %>% 
  ungroup() %>% 
  mutate(testresult_verified = case_when(
    testresult > (median_testresult + 3) & 
      testunits == "in" |
      testresult < (median_testresult - 3) & 
      testunits == "in"                         ~ NA_real_,
    testresult > (median_testresult + 5) & 
      testunits == "cm" |
      testresult < (median_testresult - 5) & 
      testunits == "cm"                         ~ NA_real_,
    TRUE                                        ~ testresult
  )) %>% 
  # select(c("patientid", testdate, testresult, median_testresult, testresult_verified,
  #          testunits, testunitscleaned, testresultcleaned, testresultcleaned_verified))
  
  mutate(height = case_when(
    !is.na(testresultcleaned_verified)          ~ round(testresultcleaned_verified / 100, 3), # cm to m
    testunits == "cm"                           ~ round(testresult_verified / 100, 3),
    testunits == "ft"                           ~ round(testresult_verified / 3.281, 3), # ft to m
    testunits == "in" | 
      !is.na(testresult)                        ~ round(testresult_verified / 39.37, 3) # in to m
    )) %>% 
  filter(!is.na(height)) %>% 
  mutate(height_units = "m") %>% 
  select(c("patientid", height_date = "testdate", "height", "height_units"))


#################################################################################################### 4 ### Cleanup of weight----
weight <- vitals %>%
  filter(test == "body weight") %>% 
  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
  # 1.Clean testresultcleaned
  group_by(patientid) %>%
  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(weight1 = case_when(
    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
    TRUE ~ NA_real_
  )) %>% 
  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
  # 2.Clean testresult to be used to find max and min
  mutate(testresult = case_when(
    testunits == "lb" &
      testresult > 12 &
      testresult < 643            ~ testresult,
    testunits == "kg" &
      testresult >= 5.5 &
      testresult < 292            ~ testresult,
    testunits == "oz" &
      testresult > 194 &
      testresult < 10286          ~ testresult,
    is.na(testunits) & 
    testresult > 5.5 & 
      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
    TRUE                          ~ NA_real_
  ))

# remove_outliers <- function(x, na.rm = TRUE, ...) { ##################### Too restrictive
#   qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
#   H <- 1 * IQR(x, na.rm = na.rm) # 1.5 remove non outliers
#   y <- x
#   y[x < (qnt[1] - H)] <- NA
#   y[x > (qnt[2] + H)] <- NA
#   y
# }

weight1 <- weight %>% 
  # 3. Calculate median for each units and remove data outside range for each patients/unit
  # 3. help distinguishing lbs to kg for same patient when unit is NA
  group_by(patientid, testunits) %>%
  mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
    testunits == "kg" &
    (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
       # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
       # F5B18C17A28F5 and F98077E9119EC FA53D0F672C7D FCFF0EDFE278F, FEF3273967DB3 wrong in cleaned too
      testresult < (median_testresult - 38.5))         ~ NA_real_, 
    testunits == "lb" &
      (testresult > (median_testresult + 99) | # choose 99 cm by default, # Problem when wrong first value FCC755E4F8722 (94.8) keep in case close to first dosinf
         testresult < (median_testresult - 99))      ~ NA_real_, # 91 for F00C16FEE3F74
    TRUE                                             ~ testresult
  )) %>%  # FCC755E4F8722 keep the first value anyway, eliminate that F8CB4CAB1073A (has 96 lbs difference-median) ?
  # mutate(cal = testresult-median_testresult)
  # mutate(difference = (median_testresultcleaned)-testresultcleaned)

  # 4. Rescue testunits when testresult_verified is close 
  # Calculate max and min to limit value for each patient-Choose 20
  group_by(patientid, testunits) %>%
  mutate(max_kg = case_when(
    testunits == "kg" ~ max(testresult_verified, na.rm = TRUE) + 20 # F181950A26A19
  )) %>%
  mutate(min_kg = case_when(
    testunits == "kg" ~ min(testresult_verified, na.rm = TRUE) - 20
  )) %>%
  mutate(max_lbs = case_when(
    testunits == "lb" ~ max(testresult_verified, na.rm = TRUE) + 30 # F14EBD0D0FA81
  )) %>%
  mutate(min_lbs = case_when(
    testunits == "lb" ~ min(testresult_verified, na.rm = TRUE) - 30
  )) %>%
  ungroup() %>% 
  group_by(patientid) %>% 
  fill(max_kg, min_kg, max_lbs, min_lbs, .direction = "downup") %>% # min_kg, max_lbs
  ungroup() %>%
  
  mutate(testunits_rescue = case_when(
    is.na(testunits) &
      testresult_verified < max_kg        ~ "kg", # Good doesn't work with F16847515CAF4 , Perfect for F8A3DD629CDA6
    is.na(testunits) & # FE8DBCAC6DAFB
      testresult_verified > min_lbs      ~ "lb" # F004D683A1695, F10CAD0F4EC48, FC109A6F719E7, FD25ED170CF07, FE06FF7C3E108, F044601199C5D
  ))

weight2 <- weight1 %>% 
  group_by(patientid) %>% 
  # 5. Rescue testunits when testresult_verified is twice or /2 means that lb or kg 
  # if is 2 times the weight in kg add lb F14EBD0D0FA81
  mutate(testunits_rescue1 = case_when(
    is.na(testunits) &
      testresult_verified < (max_kg * 2.205) &
      testresult_verified > (min_kg * 2.205)         ~ "lb",
    is.na(testunits) &
      testresult_verified < (max_lbs / 2.205) &
      testresult_verified > (min_lbs / 2.205)        ~ "kg"
  )) %>% 
  ungroup() %>% 
  mutate(testunits = coalesce(testunits, testunits_rescue, testunits_rescue1)) %>% 
  select(c("patientid", "testdate", "testunits", "testresult", "testresult_verified", "testunitscleaned", "testresultcleaned", "weight1"))

weight <- weight2 %>% 
  # 6.Fill up weight with new testresult_verified cleaned
  mutate(weight2 = case_when(
    is.na(testresultcleaned) &
      testunits == "kg"         ~ testresult_verified, # F0027D3926C88, FE8DBCAC6DAFB, F8A3DD629CDA6, F020C6A8B9E50, F16847515CAF4
    is.na(testresultcleaned) & # F044601199C5D
      testunits == "lb"         ~ (testresult_verified / 2.205), # FCB918617347C, F5E3D88009911, F14EBD0D0FA81, F16847515CAF4, FABC474931881
  )) %>% 
  mutate(weight = coalesce(weight1, weight2)) %>% 
  filter(!is.na(weight)) %>% 
  mutate(weight_units = "kg") %>% 
  select(c("patientid", weight_date = "testdate", "weight", "weight_units"))


rm(weight1, weight2, vitals)

#################################################################################################### 5 ### Cleanup of AUC----
areaUC <- auc %>% 
  filter(str_detect(drugname, "taxel|platin")) %>% 
  filter(!is.na(relativeorderedamount)) %>% 
  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
  #          "relativeorderedunits", "drugname", iscanceled)) %>%
  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
    # relativeorderedunits == "mg/kg" |
    #   relativeorderedunits == "mg" |
    #   relativeorderedunits == "m"         ~ NA_real_,
    str_detect(drugname, "taxel") &
      relativeorderedunits == "mg/m2" &
      relativeorderedamount >= 50 &
      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
    str_detect(drugname, "platin") &
      relativeorderedunits == "AUC" &
      relativeorderedamount >= 2 &
      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
    TRUE                                  ~ NA_real_
  )) %>%
  select(c("patientid", auc_date = "expectedstartdate", "target_auc", 
           auc_units = "relativeorderedunits", "drugname")) %>% 
  filter(!is.na(target_auc))


#################################################################################################### II ### Clinical Cleaning----
clinical_data <- clinical_data %>% 
  mutate(race = case_when(
    str_detect(race, "Black")    ~ "Black",
    str_detect(race, "Hispanic") ~ "White",
    TRUE                         ~ race
  )) %>% 
  mutate(ethnicity = (str_remove(ethnicity, " or Latino"))) %>% 
  unite(raceeth1, c(race,ethnicity), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
  mutate(vital = case_when(
    vitalstatus == 0     ~ "Alive",
    vitalstatus == 1     ~ "Dead"
  )) %>% 
  # mutate(aprox_month_at_os = followuptime/30.417) %>% 
  mutate(month_at_os = interval(start = diagnosisdate, end = followupdate)/
           duration(n=1, units = "months")) %>% 
  mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
  mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))


  # mutate(raceeth = case_when(
  #   str_detect(race, "NHBlack")  ~ "Non-Hispanic Black", # Black Hispanic are others?
  #   str_detect(race, "Hispanic") ~ "Hispanic White",
  #   str_detect(race, "NHWhite")  ~ "Non-Hispanic White",
  #   TRUE                         ~ raceeth
  # )) %>% 
  

# which(duplicated(drugs1))
# a <- (unique(drugs1$patientid))

#################################################################################################### II ### Treatment Cleaning----
# considered maintenance therapy : bevacizumab , olaparib, rucaparib, niraparib, gemcitabine
# Just use taxel and platin for now
# Precleaning
drugs1 <- drugs %>% 
  # 1. Filtering----
  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
  # 2. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate,episodedate, drugname, units) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  purrr::keep(~!all(is.na(.))) %>%
  ungroup() %>% 
  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need conversion
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>% 

  # 3.bind with clinical----
  full_join(., clinical_data %>% select(-c(primaryphysicianid)),
            by = "patientid") %>% 
  # Limit to the patients we have date of surgery when had surgery
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

therapy <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    issurgery == "No/unknown" &
      !is.na(episodedate)             ~ "Chemotherapy only",
    issurgery == "Yes" &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>% 
  
  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
  ungroup() %>% 
  
  # 6.Add a 30 day rule to switch linenumber----
  group_by(patientid, linenumber_new) %>% 
  arrange(episodedate) %>% 
  mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
  mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
  ungroup() %>% 
  group_by(patientid) %>% 
  mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
  mutate(linenumber_new = linenumber_new + jump_line) %>% 
  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
  
  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup()


# plot mediacation as fromtline, pie?
# Next bind the dose from orders to get AUC

therapy1 <- therapy %>% 
  select(-c("linenumber")) %>%
  arrange(episodedate) %>% 
  group_by(patientid, linenumber_new) %>%
  mutate(cycle_count_perline = min(drugname_count_perline)) %>% 
  mutate(cycle_drugname = case_when(
    cycle_count_perline == drugname_count_perline          ~ drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_drugname) %>%
  mutate(cycle_inc = row_number(cycle_drugname)) %>% 
  

  # + What to do when it is a cycle change F003F2BEEDB37 , 
  
  
  group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>%  # Problem for F001443D8B85C (make a code before recoding linenumber_new like if drugname is not in the linename remove linename)
  arrange(patientid, episodedate, cycle_inc) %>% 
  group_by(patientid, linenumber_new) %>%
  mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate, episode_interval,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>% 
  
  group_by(patientid, linenumber_new) %>% 
  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  
  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  mutate(n = row_number(drugname)) %>%

  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  fill(base_days_between_cycle, .direction = "downup") %>% 
  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  group_by(patientid, linenumber_new) %>%
  mutate(drug_count_perline = n()) %>%
  mutate(skipped_cycle_indays1 = ifelse(
    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  group_by(patientid) %>% 
  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()


rm(drugs, drugs1, therapy)


#################################################################################################### III ### Merging----
# For each feature, binding with the variable, calculate an interval between cycle date and feature dates, 
# select the smallest interval
Treatment <- 
  # Merge with creatinine
  left_join(therapy1, creatinine, by = "patientid") %>%
  mutate(interval = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>% 
  
  # Merge with height
  left_join(. , height,  by = "patientid") %>%
  mutate(interval = abs(interval(start= height_date, end= cycle_start_date)/                      
           duration(n=1, unit="days"))) %>% 
  arrange(interval) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>% 
  
  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval = abs(interval(start= weight_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%
  
  # Calculate bmi
  mutate(bmi = weight / (height * height)) %>% 
  mutate(bmi_cat = case_when(
    bmi < 25                    ~ "Underweight and normal weight",
    bmi >= 25 &
      bmi < 30                  ~ "Overweight",
    bmi >= 30                   ~ "Obese"
  )) %>% 
  # Calculate CrCl
  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
  
  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval = abs(interval(start= bsa_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>% 
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>% 
  select(-bsa_du_bois) %>% 

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  arrange(interval) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>% 
  select(-interval) %>% 
  
  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  arrange(patientid, episodedate)

# Treatment1 <- Treatment %>% 
#   select(c(patientid, "linename", "drugname", "cycle_increment", "amount", "target_auc", "auc_units", "expected_dose"))

# OrderedAmount and Quantity
# In the MedicationOrder table, ordered quantities are represented differently depending on their source. For example, orders that are placed via e-prescribing and/or flowsheet typically have OrderedAmount populated with corresponding OrderedUnits, while other medications recorded in the patient’s history typically have Quantity populated. In the majority of cases, the Quantity variable is used for medications ordered from sources other than the flowsheet and are frequently oral medications. In a relatively small number of cases, all three variables may contain distinct information; for example, an order for tamoxifen might include 20 (OrderedAmount) mg (OrderedUnits) and 30 (Quantity) capsules.
# OrderedAmount: Typically represents the dosage in mg
# Quantity: Typically represents the quantity of drug ordered in tablets or capsules
# RelativeOrderedAmount: Typically represents an order scaled to a patient’s size (for example, an order based on patient weight)
# While these variables cannot be combined, business rules can be implemented to impute the blank fields (for example, assume the recommended dose or most common days supply).

#################################################################################################### III ### Merging nand RDI----
Frontline <- Treatment %>% 
  # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
  mutate(relative_dose_intensity = round(amount/expected_dose, 3)) %>%
  group_by(patientid, chemotherapy_type, drugname) %>% 
  mutate(mean_rdi_per_drug = mean(relative_dose_intensity)) %>% 
  ungroup() %>% 
  mutate(RDI_grp = as.factor(findInterval(relative_dose_intensity, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                          levels = c("0", "1","2","3", "4", "5"), 
                          labels = c("0 < RDI < 0.75", "0.75 <= RDI < 0.85", "0.85 >= RDI < 1", "1 <= RDI < 1.5", 
                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
  mutate(delay_incare_dx_to_treat = case_when(
    str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
      duration(n=1, units = "days")),
    str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
      duration(n=1, units = "days"))
  ))

```


## Clinical summary table
```{r}
analysis_data <- Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```
<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r}
analysis_data %>% 
  select(c(race, raceeth, ethnicity, "vital",
           agecat, "ageatdx",
            
           "bmi", bmi_cat, "BSA",
           
           "histology", "groupstage", "tstage", "stagecat",
           
           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown", 
           
           "hrd_tissue", "gis_tissue")) %>% 
  tbl_summary() %>% bold_labels()
```

<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
```{r}
analysis_data %>% 
  select(c(race, raceeth, ethnicity, "vital",
           agecat, "ageatdx",
            
           "bmi", bmi_cat, "BSA",
           
           "histology", "groupstage", "tstage", "stagecat",
           
           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown", 
           
           "hrd_tissue", "gis_tissue")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
```

## Treatment summary table
<span style="color:green">**Table 3 Summary treatment data by race**</span>

```{r}
tbl1 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "relative_dose_intensity", "RDI_grp")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           "chemotherapy_type", "therapy", "treatment_sequence", "relative_dose_intensity", "RDI_grp")) %>% 
  tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
```{r}
# Treatment & demo
tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl3 <- 
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl4 <- 
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl5 <- 
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
  filter(exclude != "1") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>% 
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_p()
tbl6 <- 
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl_stack(list(tbl3, tbl4, tbl5, tbl6))
```



## Survivals
### OS by clinical

<span style="color:green">**Survival plots**</span>

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by race
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by histology
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ tstage, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by brca1_germline
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by brca2_germline
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

### OS by treatment

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by issurgery
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by extentofdebulking
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by residualdiseasestatus
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by chemotherapy_type
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by chemo
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by therapy
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE) %>% 
                     filter(exclude != "1")),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))

# OS by RDI_grp for platin
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "platin")) %>% 
                     
                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# OS by RDI_grp for taxel
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
                     
                     distinct(patientid, .keep_all = TRUE)), 
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>


## HR
<span style="color:green">**Table 5 HR**</span>

```{r, echo=TRUE}
model <- coxph(Surv(time = month_at_os, 
                     event = vitalstatus)~RDI_grp, 
                data = Frontline %>% 
                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
                     distinct(patientid, .keep_all = TRUE))
summary(model)
```



## Regression

```{r include=TRUE}
# Regression vital status prediction
model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

# extentofdebulking + residualdiseasestatus + 

model <- glm(vitalstatus ~ 
               histology + tstage + brca1_tumor + brca2_tumor + 
             issurgery +
             chemotherapy_type, 
             data = analysis_data, family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))


# Regression RDI prediction
model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline %>% 
               distinct(patientid, .keep_all = TRUE) %>% 
               filter(exclude != "1"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

#  for carbo
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
               distinct(patientid, .keep_all = TRUE) %>% 
               filter(exclude != "1"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
               distinct(patientid, .keep_all = TRUE) %>% 
               filter(exclude != "1"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

# tbl5 <- 
  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**Adjuvant**", "**Neoadjuvant**"))

#  for taxel
model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")) %>% 
               distinct(patientid, .keep_all = TRUE) %>% 
               filter(exclude != "1"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")) %>% 
               distinct(patientid, .keep_all = TRUE) %>% 
               filter(exclude != "1"), family = binomial)
tbl1 <- tbl_regression(model)
tbl2 <- tbl_regression(model, exponentiate = TRUE)
tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))

# tbl6 <- 
  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**Adjuvant**", "**Neoadjuvant**"))
```

## Extra plots linenumber 1
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>%
  filter(linenumber_new == "1") %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

analysis_data %>% 
    filter(linenumber_new == "1") %>% 
  group_by(chemotherapy_type) %>% 
  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
  geom_bar(stat="identity")+
  labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
analysis_data %>% 
  filter(linenumber_new == "1") %>% 
  group_by(treatment_sequence) %>% 
  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
  geom_bar(stat="identity")+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()

# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= chemo))+
#   geom_bar()+
#   theme_minimal()+
#   coord_flip()
```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r}
# What are the RDI distribution for each type of chemo
print("A quick summary for the RDI repartition")
analysis_data2 <- analysis_data %>% filter(linenumber_new == "1")
summary(analysis_data2$relative_dose_intensity)
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_boxplot()+
  geom_jitter(shape=16)+
  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
  theme_minimal()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(linenumber_new == "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  # geom_boxplot()+
  ylim(c(-.5, 3.5))+
  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
  theme_minimal() +
  guides(color=FALSE)

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(linenumber_new == "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_violin()+
  ylim(c(-.5, 3.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()
```
</div>

<div class = "col-md-6">
```{r}
# What are the RDI distribution for each drug
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(linenumber_new == "1") %>% 
  ggplot(aes(x= drugname, y= relative_dose_intensity))+
  geom_violin(aes(color=relative_dose_intensity<0.85))+
  ylim(c(-.5, 5.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()+
  coord_flip()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(linenumber_new == "1") %>% 
  ggplot(aes(x= RDI_grp, fill = drugname))+
  geom_bar()+
  theme_minimal()+
  coord_flip()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(linenumber_new == "1") %>% 
  ggplot(aes(x= RDI_grp, fill = drugname))+
  geom_bar(position = "fill")+
  theme_minimal()+
  coord_flip()
```
</div>
</div>

## Extra plots all line together

<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  group_by(chemotherapy_type) %>% 
  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
  geom_bar(stat="identity")+
  labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  group_by(treatment_sequence) %>% 
  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
  geom_bar(stat="identity")+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()

# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= chemo))+
#   geom_bar()+
#   theme_minimal()+
#   coord_flip()
```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r}
# What are the RDI distribution for each type of chemo
print("A quick summary for the RDI repartition")
summary(analysis_data$relative_dose_intensity)
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_boxplot()+
  geom_jitter(shape=16)+
  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
  theme_minimal()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  # geom_boxplot()+
  ylim(c(-.5, 3.5))+
  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
  theme_minimal() +
  guides(color=FALSE)

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
  geom_violin()+
  ylim(c(-.5, 3.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()
```
</div>
</div>

<div class = "row">
<div class = "col-md-6">
```{r}
# What are the RDI distribution for each drug
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= drugname, y= relative_dose_intensity))+
  geom_violin(aes(color=relative_dose_intensity<0.85))+
  ylim(c(-.5, 5.5))+
  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
  theme_minimal()+
  coord_flip()

Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= RDI_grp, fill = drugname))+
  geom_bar()+
  theme_minimal()+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
  filter(exclude != "1") %>% 
  ggplot(aes(x= RDI_grp, fill = drugname))+
  geom_bar(position = "fill")+
  theme_minimal()+
  coord_flip()
```
</div>
</div>




